---
title: "R Notebook"
output: html_notebook
---

Checar directorio de trabjo

```{r}
getwd()
```

```{r}

setwd("/Users/softcomputing/Ciencia_de_los_datos")
```

```{r}
conclaves<-read.csv("Conclaves.csv")
```


```{r}
head(conclaves)
```

```{r}
str(conclaves)
```

Conclave	Estadístico
1903	    conclave1
1914	    conclave2
1922	    conclave3
1939	    conclave4
1958	    conclave5
1963	    conclave6
1978	    conclave7
1978	   conclave8
2005	    conclave9
2013	    conclave10

```{r}
conclave1<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1903",]
```

```{r}
View(conclave1)
```
```{r}
View(conclave1)
```

```{r}
# CLASIFICACIÓN
conclave2<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1914",]
conclave3<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1922",]
conclave4<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1939",]
conclave5<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1958",]
conclave6<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1963",]
conclave7<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1978" & conclaves$NOMBRE.DEL.CARDENAL!="John Joseph Wright",]
conclave8<-conclaves[conclaves$A.O.DE.PARTICIPACION=="1978" & conclaves$NOMBRE.DEL.CARDENAL!="Albino Luciani",]
conclave9<-conclaves[conclaves$A.O.DE.PARTICIPACION=="2005",]
conclave10<-conclaves[conclaves$A.O.DE.PARTICIPACION=="2013",]
```


```{r}
View(conclave8)
```


```{r}
# RESUMEN DATOS
summary(conclave1$EDAD.AL.PARTICIPAR)
summary(conclave2$EDAD.AL.PARTICIPAR)
summary(conclave3$EDAD.AL.PARTICIPAR)
summary(conclave4$EDAD.AL.PARTICIPAR)
summary(conclave5$EDAD.AL.PARTICIPAR)
summary(conclave6$EDAD.AL.PARTICIPAR)
summary(conclave7$EDAD.AL.PARTICIPAR)
summary(conclave8$EDAD.AL.PARTICIPAR)
summary(conclave9$EDAD.AL.PARTICIPAR)
summary(conclave10$EDAD.AL.PARTICIPAR)
```
```{r}
# OBYIENER DESVIACIÓN ESTÁNDAR
sd(conclave1$EDAD.AL.PARTICIPAR)/mean(conclave1$EDAD.AL.PARTICIPAR)
sd(conclave2$EDAD.AL.PARTICIPAR)/mean(conclave2$EDAD.AL.PARTICIPAR)
sd(conclave3$EDAD.AL.PARTICIPAR)/mean(conclave3$EDAD.AL.PARTICIPAR)
sd(conclave4$EDAD.AL.PARTICIPAR)/mean(conclave4$EDAD.AL.PARTICIPAR)
sd(conclave5$EDAD.AL.PARTICIPAR)/mean(conclave5$EDAD.AL.PARTICIPAR)
sd(conclave6$EDAD.AL.PARTICIPAR)/mean(conclave6$EDAD.AL.PARTICIPAR)
sd(conclave7$EDAD.AL.PARTICIPAR)/mean(conclave7$EDAD.AL.PARTICIPAR)
sd(conclave8$EDAD.AL.PARTICIPAR)/mean(conclave8$EDAD.AL.PARTICIPAR)
sd(conclave9$EDAD.AL.PARTICIPAR)/mean(conclave9$EDAD.AL.PARTICIPAR)
sd(conclave10$EDAD.AL.PARTICIPAR)/mean(conclave10$EDAD.AL.PARTICIPAR)
```


Pio X 68
Benedicto XVI 56
Pio XI 65
Pio XII 63
Juan XXIII 77
Pablo VI 66
Juan Pablo I 65
Juan Pablo II 56
Benedicto XVI 78
Francisco 76



mi_df <- data.frame(
  "entero" = 1:4, 
  "factor" = c("a", "b", "c", "d"), 
  "numero" = c(1.2, 3.4, 4.5, 5.6),
  "cadena" = as.character(c("a", "b", "c", "d"))
)
```{r}
papas<-data.frame(
  Nombre=c("PioX","BenedictoXV","PioXI", "PioXII","JuanXXIII","PabloVI","Juan PabloI","Juan PabloII","BenedictoXVI","Francisco"),
  Edad=c(68,56,65,63,77,66,65,56,78,76))
```

```{r}
head(papas)
str(papas)
mean(papas$Edad)
sd(papas$Edad)/mean(papas$Edad)
```

```{r}
help("barplot")
```


```{r}

barplot(papas$Edad,names.arg = papas$Nombre,horiz = TRUE,las=1, xlim=c(0, 80))
```

orden<-reorder(papas$Nombre,papas$Edad,max)
```{r}
library(ggplot2)
```

library(ggplot2)
# Basic barplot
p<-ggplot(data=df, aes(x=dose, y=len)) +
  geom_bar(stat="identity")
p
   
# Horizontal bar plot
p + coord_flip()
x=reorder(Parcela,-Plantas)


ggplot(data=df, aes(x=reorder(Parcela,-Plantas), y=Plantas, fill=Tratamiento)) 

```{r}

p<-ggplot(data=papas,aes(x=reorder(Nombre,-Edad),y=Edad)) + geom_bar(stat="identity",position="dodge")+theme(panel.grid = element_blank())
p

```



```{r}
p + coord_flip()+theme(panel.grid = element_blank())
```


```{r}
p<-ggplot(data=papas,aes(x=reorder(Nombre,Edad),y=Edad)) + geom_bar(stat="identity",position="dodge")
p
```

```{r}
p<-p+coord_flip() +theme(panel.grid = element_blank())
```

```{r}
p<-ggplot(data=papas,aes(x=reorder(Nombre,-Edad),y=Edad)) + geom_bar(stat="identity",position="dodge")
p+coord_flip()
p
```
```{r}
p+theme(panel.background = element_rect(fill = 'white'))
```

```{r}

PromedioConclave<-data.frame(
  Reunion=c("Conclave1","Conclave2","Conclave3", "Conclave4","Conclave5","Conclave6","Conclave7","Conclave8","Conclave9","Conclave10"),
  PEdad=c(mean(conclave1$EDAD.AL.PARTICIPAR),mean(conclave2$EDAD.AL.PARTICIPAR),mean(conclave3$EDAD.AL.PARTICIPAR),mean(conclave4$EDAD.AL.PARTICIPAR),mean(conclave5$EDAD.AL.PARTICIPAR),mean(conclave6$EDAD.AL.PARTICIPAR),mean(conclave7$EDAD.AL.PARTICIPAR),mean(conclave8$EDAD.AL.PARTICIPAR),mean(conclave9$EDAD.AL.PARTICIPAR),mean(conclave10$EDAD.AL.PARTICIPAR)))

```

```{r}
p<-ggplot(data=PromedioConclave,aes(x=reorder(Reunion,-PEdad),y=PEdad)) + geom_bar(stat="identity",position="dodge")
p+coord_flip()
p
```
```{r}
hist(conclave5$EDAD.AL.PARTICIPAR)
```
```{r}
hist(conclaves$EDAD.AL.PARTICIPAR)
```

```{r}
hist(conclave9$EDAD.AL.PARTICIPAR)
```


```{r}
View(PromedioConclave)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

