---
title: "R Notebook"
output: html_notebook
---

/Users/softcomputing/ciencia de datos
```{r}
library(rvest)
```


```{r}
webpage <- read_html("https://es.wikipedia.org/wiki/Anexo:Cardenales")
```


```{r}
tablas <- html_table(webpage) 
class(tablas)
tablas
```

```{r}
consistorio1=(tablas[[1]])
consistorio2=(tablas[[2]])
consistorio3=(tablas[[3]])

# ELIMINANDO COLUMNAS
consistorio1$Fotografía <- NULL
consistorio2$Fotografía <- NULL
consistorio3$Fotografía <- NULL

consistorio1$Escudo <- NULL
consistorio2$Escudo <- NULL
consistorio3$Escudo <- NULL

```

```{r}
View(consistorio1)
```

```{r}
write.csv(consistorio1,"nuevoconsistorio.csv")
write.csv(consistorio2,"electores.csv")
write.csv(consistorio3,"noelectores.csv")
```


```{r}


```


```{r}
consistorio2
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

